---
title: "Rplot_NLS_KDD"
author: "MarkSniper94"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
kdd <- read.csv("train_NLS_KDD.csv")
```

#Exploratory data analysis KDD Dataset

Caret library is used to show some graphics.
```{r  , results="hide"}
library(caret)
```

Now, character variables are considered. 
```{r}
Charcol <- names(kdd[,sapply(kdd, is.factor)])
print(Charcol)
print(unique(kdd$result))#result of attack
print(unique(kdd$service))#network service on the destination, e.g., http, telnet, etc.
print(unique(kdd$flag))#normal or error status of the connection
print(unique(kdd$protocol_type))#type of the protocol, e.g. tcp, udp, etc.
```

Plot mean attack duration and median attack duration.
```{r}
ggplot(data=kdd, aes(x=kdd$result, y=kdd$duration, fill = kdd$result)) + 
  geom_bar(stat = "summary", fun.y = "mean")+scale_x_discrete(name = "Attack")+
  scale_y_continuous("Duration")+labs(title="Mean attack duration", fill=("Attack\n") )

#median attack duraction
ggplot(data=kdd, aes(x=kdd$result, y=kdd$duration, fill = kdd$result)) + 
  geom_bar(stat = "summary", fun.y = "median")+scale_x_discrete(name = "Attack")+
  scale_y_continuous("Duration")+labs(title="Median attack duration", fill=("Attack\n") )
```

The graphs show that the average durations reflect the type of attack. 

Plot average duration of attacks based on the type of protocol.
```{r}
ggplot(data=kdd, aes(x=kdd$result, y=kdd$duration, fill = kdd$protocol_type)) + 
  geom_bar(stat = "summary", fun.y = "mean")+scale_x_discrete(name = "Attack")+
  scale_y_continuous("Duration")+ scale_fill_discrete(name = "Protocol type\n")+
  labs(title="Average duration of attacks based on the type of protocol" )
```

As can be seen from the graph, the types of attacks reflect the average duration based on the type of protocol. In fact, many attacks use the TCP protocol that is widely used to implement different services.

Individual observations using duration, attack and protocol type.
```{r}
p1 <- ggplot(kdd,aes(y = kdd$duration, x = kdd$result)) +
  geom_point()
p1 +  geom_point(aes(color=kdd$protocol_type))+
  labs(title="Duraction, attack and protocol type" , color ="Protocol type")+
  scale_x_discrete(name = "Attack")+
  scale_y_discrete("Duration")
```

The previous graph shows the absence of outliers in character variables, since the individual observations are very close to each other and correlated according to the type of attack.

Now, the service average is considered based on the type of attack and protocol.
```{r}
ggplot(data=kdd, aes(x=kdd$service, y=kdd$result, fill = kdd$protocol_type)) + 
  geom_bar(stat = "summary", fun.y = "mean")+scale_x_discrete(name = "Service")+
  scale_y_discrete("Attack")+ scale_fill_discrete(name = "Protocol type\n")+
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  labs(title="Average duration of attacks based on the type of protocol" )
```

Finally, flag feature is analyzed respect types of attack and services. 
```{r}
p1 <- ggplot(kdd,aes(y = kdd$flag, x = kdd$service)) +
  geom_point()
p1 +  geom_point(aes(color=kdd$result))+
  labs(title="Duraction, attack and protocol type" , color ="Attack\n")+
  scale_x_discrete(name = "Service")+
  scale_y_discrete("Falg")+ theme(axis.text.x=element_text(angle=90,hjust=1))
```

Analyzing the graphs, it is possible to conclude that the dataset is correct. Furthermore, the various graphs show the absence of outliers. Despite all the numerical variables are uncorrelated, the character variables do not highlight any outliers, since the individual observations are very close to each other.

Finally, the type of service frequency is proposed, since the frequency of the ICMP protocol is not shown perfectly in the previous graphs.
```{r}
quantity <- as.data.frame(table(kdd$protocol_type))
head(quantity)
bp<- ggplot(quantity, aes(x="", y=Freq, fill=Var1))+
  geom_bar(width = 1, stat = "identity")
pie <- bp +  coord_polar(theta = "y")+
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank())+ scale_fill_discrete(name = "Protocol type")+ 
  labs(title = "Protcol type frequency")+
  labs(x = "", y = "");
pie
```

To conclude with the character variables, a graph for each individual observation is shown below.
```{r}
p1 <- ggplot(kdd,aes(y = kdd$flag, x = kdd$service)) +
  geom_point()
p1 +  geom_point(aes(color=kdd$protocol_type, shape =kdd$result))+
  labs(title="All character variables\n\n" , color ="Protocol type",shape="Attack")+
  scale_x_discrete(name = "Service")+
  scale_y_discrete("Falg")+theme(axis.text.x=element_text(angle=90,hjust=1))
```

```{r}
#show all occurrence flag
tcp_flag <- kdd[, 2:4]
tcp_flag <- tcp_flag[, -2]
table(tcp_flag)
```

For the analysis of numerical variables, all the histograms of each individual numerical variable are shown. It can be noted that the various distributions of the numerical variables are uncorrelated to each other, in fact, their covariance is zero, and a random process has not generated them.
```{r}
kdd_numeric <- kdd[,-2]#remove protocol type
kdd_numeric <- kdd_numeric[,-2]#remove service
kdd_numeric <- kdd_numeric[,-2]#remove flag
str(kdd_numeric)
colNam <- colnames(kdd_numeric)
print(colNam)

qplot(duration,fill=result,data=kdd_numeric, bins = 30)

qplot(src_bytes,fill=result,data=kdd_numeric, bins = 30)

qplot(dst_bytes,fill=result,data=kdd_numeric, bins = 30)

qplot(land,fill=result,data=kdd_numeric, bins = 30)

qplot(wrong_fragment,fill=result,data=kdd_numeric, bins = 30)

qplot(urgent,fill=result,data=kdd_numeric, bins = 30)

qplot(hot,fill=result,data=kdd_numeric, bins = 30)

qplot(num_failed_logins,fill=result,data=kdd_numeric, bins = 30)

qplot(logged_in,fill=result,data=kdd_numeric, bins = 30)

qplot(num_compromised,fill=result,data=kdd_numeric, bins = 30)

qplot(root_shell,fill=result,data=kdd_numeric, bins = 30)

qplot(su_attempted,fill=result,data=kdd_numeric, bins = 30)

qplot(num_root,fill=result,data=kdd_numeric, bins = 30)

qplot(num_file_creations,fill=result,data=kdd_numeric, bins = 30)

qplot(num_shells,fill=result,data=kdd_numeric, bins = 30)

qplot(num_access_files,fill=result,data=kdd_numeric, bins = 30)

qplot(num_outbound_cmds,fill=result,data=kdd_numeric, bins = 30)

qplot(is_hot_login,fill=result,data=kdd_numeric, bins = 30)

qplot(is_guest_login,fill=result,data=kdd_numeric, bins = 30)

qplot(count,fill=result,data=kdd_numeric, bins = 30)

qplot(srv_count,fill=result,data=kdd_numeric, bins = 30)

qplot(serror_rate,fill=result,data=kdd_numeric, bins = 30)

qplot(srv_serror_rate,fill=result,data=kdd_numeric, bins = 30)

qplot(rerror_rate,fill=result,data=kdd_numeric, bins = 30)

qplot(srv_rerror_rate,fill=result,data=kdd_numeric, bins = 30)

qplot(same_srv_rate,fill=result,data=kdd_numeric, bins = 30)

qplot(diff_srv_rate,fill=result,data=kdd_numeric, bins = 30)

qplot(srv_diff_host_rate,fill=result,data=kdd_numeric, bins = 30)

qplot(dst_host_count,fill=result,data=kdd_numeric, bins = 30)

qplot(dst_host_srv_count,fill=result,data=kdd_numeric, bins = 30)

qplot(dst_host_same_srv_rate,fill=result,data=kdd_numeric, bins = 30)

qplot(dst_host_diff_srv_rate,fill=result,data=kdd_numeric, bins = 30)

qplot(dst_host_same_src_port_rate,fill=result,data=kdd_numeric, bins = 30)

qplot(dst_host_srv_diff_host_rate,fill=result,data=kdd_numeric, bins = 30)

qplot(dst_host_serror_rate,fill=result,data=kdd_numeric, bins = 30)

qplot(dst_host_srv_serror_rate,fill=result,data=kdd_numeric, bins = 30)

qplot(dst_host_rerror_rate,fill=result,data=kdd_numeric, bins = 30)

qplot(dst_host_srv_rerror_rate,fill=result,data=kdd_numeric, bins = 30)

```